### 2021-07-20 README.Rmd
added do_condition and compareCPUE. Some incomplete developments underway. No EWN

>>>>

* 2021-07-20 aMSE 0.0.0.900 Added do_condition and compareCPUE. Both used to speed the conditioning of the operating model, though a number of developments are still under development. Currently can automatically search for the AvRec value that will optimize the sum-of-squared residual fit between the
observed CPUE in the historical period, and those predicted by the conditioned model. The undeveloped bit related to the ad hoc recruitment deviates.
